
# Recreating the boosted classification trees from the charity predictions project in PREDICT 422

## Read in the data
Need to drop the `id` column so it's not used in any splitting process
```{r}
library(dplyr)
library(readr)
dat <- read_csv('raw_data.csv')%>%
  select(-id)%>%
  
dat
```

## Classification 
```{r}
library(gbm)
class.fit <- gbm(formula = donor ~., data = dat%>%select(-damt),
                 distribution = 'bernoulli',
                 n.trees = 10000,
                 interaction.depth = 4)

class.pred <- predict(class.fit,
                      newdata = dat%>%select(-damt),
                      n.trees = 10000,
                      type = 'response')

class.fit.sum <- summary(class.fit)
```

# Model evaluation

First, for each model, I want to see how much each variable impacted the prediction by showing bar charts of how often each variable was used as a split.
```{r}
library(ggplot2)
library(yaztheme)

var_imp <- ggplot(class.fit.sum, aes(x = reorder(var, rel.inf), y = rel.inf))+
  geom_col(fill = yaz_cols[3])+
  labs(title = 'Variable Importance',
       y = 'Percentage of Splits Using Variable',
       x = element_blank())+
  coord_flip()+
  theme_yaz()
ggsave('Variable Importance by Model.pdf', height = 4, width = 6)
```

Now to evaluate the classification accuracy by plotting the distribution of probabilities compared to actual values and then measure actual classification error

```{r}
class.acc.df <- data.frame(actual = dat$donor, predicted = class.pred)%>%
  mutate(win = ifelse(actual == round(predicted),1,0))
ggplot(class.acc.df, aes(x = predicted*100, fill = as.character(actual)))+
  geom_density(alpha = .7)+
  scale_fill_manual(name = 'Donor', labels = c('No','Yes'), 
                    values = yaz_cols[3:4])+
  labs(title = 'Distribution of Donation Predictions',
       y = 'Density',
       x = 'Predicted Donation Likelihood')+
  theme_yaz()
ggsave('Distribution of Donation Predictions.pdf', width = 6, height = 4)
```

Calcualte profit assuming the average donor gives \$14.50 and each letter costs \$2. It's not enough to just set the cutoff at 50% donation likelihood, you need to set the cutoff at the point of diminishing marginal return.
```{r}
class.cum.prof <- class.acc.df%>%
  arrange(desc(predicted))%>%
  mutate(profit = ifelse(actual == 1, 12.5, -2),
         total_profit = cumsum(profit))

max.prof <- max(class.cum.prof$total_profit)
maximizing.prob <- class.cum.prof$predicted[class.cum.prof$total_profit == max.prof]

sum(class.cum.prof$profit)
ggplot(class.cum.prof, aes(x = predicted*100, y = total_profit))+
  geom_line(color = yaz_cols[4])+
  scale_x_reverse()+
  geom_vline(xintercept = maximizing.prob*100, linetype = 'dashed')+
  annotate('text', x = 75, y = 100, label = 'Mail')+
  annotate('text', x = 15, y = 100, label = 'Do Not Mail')+
  # annotate('text', x = 65, y = max.prof, label = '')+
  labs(title = 'Cumulative Profit by Donation Likelihood',
       subtitle = 'Predicted maximum profit is $35,294 mailing to modeled donors only compared to $31,409 mailing to everyone',
       x = 'Donation Likelihood (Predicted)',
       y = 'Total Profit')+
  theme_yaz()
ggsave('Cumulative Profit by Donation Likelihood.pdf', width = 8, height = 5)
```