---
title: "R Notebook"
output: html_notebook
---

Instructions for scraping unofficial election results from sbe.virginia.gov

Step 1: Scrape the results by county page to get a list of all county names, then use that to create a list urls for precinct level results.

```{r}
library(rvest)
library(dplyr)

base_page <- 'http://results.elections.virginia.gov/vaelections/2017%20November%20General/Site/Governor.html'

html_base <- read_html(base_page)

counties <- html_base%>%html_nodes('h2 span')%>%html_text()
counties <- counties[3:length(counties)]
head(counties)
```

Next we need to loop through each county to collect results for Governor
```{r}
library(rjson)
library(RCurl)

gov_getter <- function(year){
  county_data <- list()
  for(i in seq(1, length(counties))){
    pre <- paste0('http://results.elections.virginia.gov/vaelections/',year,'%20November%20General/Json/Locality/')
    gpost <-'/Governor.json'
    govjson <- fromJSON(httpGET(paste0(pre,gsub(' ','%20',counties[i]),gpost))) 
    
    mid_df <- list()
    for(p in seq(1,length(govjson$Precincts))){
      candidate_name <- c()
      party <- c()
      ballot_order <- c()
      votes <- c()
      county <- c()
      precinct <- c()   
      for(c in seq(1,length(govjson$Precincts[[p]]$Candidates))){
        candidate_name[c] <- govjson$Precincts[[p]]$Candidates[[c]]$BallotName%>%as.character()
        party[c] <- govjson$Precincts[[p]]$Candidates[[c]]$PoliticalParty%>%as.character()
        ballot_order[c] <- govjson$Precincts[[p]]$Candidates[[c]]$BallotOrder%>%as.character()
        votes[c] <- govjson$Precincts[[p]]$Candidates[[c]]$Votes%>%as.character()
        county[c] <- govjson$Locality$LocalityName%>%as.character()
        precinct[c] <- govjson$Precincts[[p]]$PrecinctName%>%as.character()
      }
      mid_df[[p]] <- data.frame(candidate_name, party, ballot_order, votes, county, precinct)
    }
    county_data[[i]] <- bind_rows(mid_df)
  }
  return(bind_rows(county_data))
}

gov17 <- gov_getter(2017)
```

Now we want to do the same for House of Delegates races which use a slightly different url structure
```{r}
hod_getter <- function(year){
  dist_dfs<- list()
  for(i in seq(1, 100)[-c(11, 32, 35, 36, 27, 38, 39, 41, 42, 43, 44, 46, 47, 51, 52, 72,73,78,82,84,85, 89, 92, 94)]){
    if(i < 10){
      char_i <- paste0('00',i)
    } else if(i < 100){
      char_i <- paste0('0',i)
    } else {
      char_i <- as.character(i)
    }
    first <- paste0('http://results.elections.virginia.gov/vaelections/',
                    year,
                    '%20November%20General/Site/Member%20House%20of%20Delegates%20(',
                    char_i,').html')
    # print(first)
    hod_counties <- read_html(first)%>%html_nodes('h2 span')%>%html_text()
    hod_counties <- hod_counties[3:length(hod_counties)]
    # print(hod_counties)
    county_data <- list()
    for(h in seq(1,length(hod_counties))){
      pre <- paste0('http://results.elections.virginia.gov/vaelections/',year,'%20November%20General/Json/Locality/')
      post <- paste0('/Member%20House%20of%20Delegates%20(',char_i,').json')
      print(paste0(pre,gsub(' ','%20',hod_counties[h]),post))
      govjson <- fromJSON(httpGET(paste0(pre,gsub(' ','%20',hod_counties[h]),post)))
      mid_df <- list()
      for(p in seq(1,length(govjson$Precincts))){
        candidate_name <- c()
        party <- c()
        ballot_order <- c()
        votes <- c()
        county <- c()
        precinct <- c()   
        for(c in seq(1,length(govjson$Precincts[[p]]$Candidates))){
          candidate_name[c] <- govjson$Precincts[[p]]$Candidates[[c]]$BallotName%>%as.character()
          party[c] <- govjson$Precincts[[p]]$Candidates[[c]]$PoliticalParty%>%as.character()
          ballot_order[c] <- govjson$Precincts[[p]]$Candidates[[c]]$BallotOrder%>%as.character()
          votes[c] <- govjson$Precincts[[p]]$Candidates[[c]]$Votes%>%as.character()
          county[c] <- govjson$Locality$LocalityName%>%as.character()
          precinct[c] <- govjson$Precincts[[p]]$PrecinctName%>%as.character()
          }
        mid_df[[p]] <- data.frame(candidate_name, party, ballot_order, votes, county, precinct)
      }
      county_data[[h]] <- bind_rows(mid_df)
    }
    dist_dfs[[i]] <- bind_rows(county_data)
  }
  return(bind_rows(dist_dfs))
}

# hod13 <- hod_getter(2013)
hod17 <- hod_getter(2017)
# http://results.elections.virginia.gov/vaelections/2017%20November%20General/Json/Locality/LEE%20COUNTY/Member%20House%20of%20Delegates%20(001).json
```

The rest of the house races all come from one locality so we can skip a step above and still have a super janky loop!
```{r}
dels <- read_html('http://results.elections.virginia.gov/vaelections/2017%20November%20General/Site/GeneralAssembly.html')
links <- dels%>%html_nodes('h2 a')%>%html_attr('href')
links <- gsub('.html','.json', gsub(' ','%20',links[grepl('Locality', links)]))

dist_dfs<- list()
for(i in seq(1, length(links))){
  url <- gsub('Json.','Json', paste0('http://results.elections.virginia.gov/vaelections/2017%20November%20General/Json',links[i]))
  # print(first)
  # print(hod_counties)
  race <- fromJSON(getURL(url))
  county_data <- list()
  for(p in seq(1,length(race$Precincts))){
    candidate_name <- c()
    party <- c()
    ballot_order <- c()
    votes <- c()
    county <- c()
    precinct <- c()   
    for(c in seq(1,length(race$Precincts[[p]]$Candidates))){
      candidate_name[c] <- race$Precincts[[p]]$Candidates[[c]]$BallotName%>%as.character()
      party[c] <- race$Precincts[[p]]$Candidates[[c]]$PoliticalParty%>%as.character()
      ballot_order[c] <- race$Precincts[[p]]$Candidates[[c]]$BallotOrder%>%as.character()
      votes[c] <- race$Precincts[[p]]$Candidates[[c]]$Votes%>%as.character()
      county[c] <- race$Locality$LocalityName%>%as.character()
      precinct[c] <- race$Precincts[[p]]$PrecinctName%>%as.character()
    }
    county_data[[p]] <- data.frame(candidate_name, party, ballot_order, votes, county, precinct)
  }
  dist_dfs[[i]] <- bind_rows(county_data)
}
fullhod17 <- bind_rows(hod17, bind_rows(dist_dfs))

```

Scraping the registration stats for each precinct in 2017
```{r}
reg_pages <- read_html('http://results.elections.virginia.gov/vaelections/2017%20November%20General/Site/Statistics/Registration.html')%>%
  html_nodes('td a')%>%
  html_attr('href')

counties <- list()
for(i in seq(1, length(reg_pages))){
  link <- gsub(' ', '%20', paste0('http://results.elections.virginia.gov/vaelections/2017%20November%20General/Site/Statistics/',reg_pages[i]))
  counties[[i]] <- read_html(link)%>%html_table()
}
rvs17 <- bind_rows(counties)

counties[[1]]%>%as.data.frame()
clean_counties <- list()
for(i in seq(1,length(counties))){
  clean_counties[[i]] <- as.data.frame(counties[[i]])%>%
    dplyr::select(precinct = Precinct, active = Active.Voter.Count, inactive = Inactive.Voter.Count, total = Total.Voter.Count)%>%
    mutate(precinct = as.character(precinct), active = as.numeric(gsub(',','',active)), 
           inactive = as.numeric(gsub(',','',inactive)), total = as.numeric(gsub(',','',total)))
}
rvs <- bind_rows(clean_counties)
```

Now to make sense of all this non-sense and connect the datasets together! 

```{r}
flat_gov <- gov17%>%
  mutate(democrat = ifelse(as.character(party) == 'Democratic', as.numeric(gsub(',','',votes)), NA),
         republican = ifelse(as.character(party) == 'Republican', as.numeric(gsub(',','',votes)), NA),
         other = ifelse(!as.character(party) %in% c('Democratic','Republican'), as.numeric(gsub(',','',votes)), NA),
         precinct = substring(precinct, 1, nchar(precinct)-5))%>%
  group_by(precinct, county)%>%
  summarise(democrat = sum(democrat, na.rm = T),
            republican = sum(republican, na.rm = T),
            other = sum(other, na.rm = T))%>%
  mutate(office = 'Governor')

flat_hod <- fullhod17%>%
  mutate(democrat = ifelse(as.character(party) == 'Democratic', as.numeric(gsub(',','',votes)), NA),
         republican = ifelse(as.character(party) == 'Republican', as.numeric(gsub(',','',votes)), NA),
         other = ifelse(!as.character(party) %in% c('Democratic','Republican'), as.numeric(gsub(',','',votes)), NA),
         precinct = substring(precinct, 1, nchar(precinct)-6))%>%
  group_by(precinct, county)%>%
  summarise(democrat = sum(democrat, na.rm = T),
            republican = sum(republican, na.rm = T),
            other = sum(other, na.rm = T))%>%
  mutate(office = 'House of Delegates')#, test = substring(precinct, nchar(precinct)-5, nchar(precinct)))

contested_precincts <- flat_hod%>%
  mutate(dem.two.way = democrat*100/(democrat+republican),
         contested = ifelse(between(dem.two.way, 10, 90), 'contested','uncontested'))%>%
  filter(contested == 'contested')%>%
  .$precinct
results.a <- bind_rows(flat_gov, flat_hod)%>%
  left_join(rvs)%>%
  filter(!is.na(active))%>%
  mutate(dem.two.way = democrat*100/(democrat+republican),
         turnout = (democrat + republican + other)*100/active)

contested_precincts <- results.a%>%
  filter(office == 'House of Delegates',
         between(dem.two.way, 10, 90))%>%
  .$precinct

results <- results.a%>%
  mutate(hod_contested = ifelse(precinct %in% contested_precincts, 1,0))

write.csv(results, 'results.csv')
```













































