---
title: "How Mad Is March?"
output: html_notebook
---

This notebook contains code for a few attempts I took at quantifying the madness in March. This analysis focuses primarily on seeding as a predictor because I was too lazy to scrape all the data from 1985 onward or connect my own data to this!

# Read Data and Packages
```{r}
library(MASS)
library(tidyverse)
library(yaztheme)
library(ggridges)
results <- read_csv('results_1985_2017.csv')%>%
  mutate(lower_seed_win = ifelse(winner_seed < not_winner_seed, 1, 0),
         lower_seed_spread = ifelse(winner_seed < not_winner_seed, 
                                    winner_points - not_winner_points, 
                                    not_winner_points - winner_points))
matchups <- read_csv('matchups.csv')
chart_cap <- 'Data | Sports Reference\nChart | Josh Yazman (@jyazman2012)'
```

# How Likely is the Lower Seed to Win One Game?
The selection committee has been historically good at seeding teams. 
```{r}
ggplot(results, aes(x = lower_seed_spread, y = as.character(year)))+
  geom_vline(xintercept = 0, linetype = 'dashed')+
  geom_density_ridges(fill = yaz_cols[1], alpha = .7)+
  labs(title = 'Point Spreads for Lower Seeded Team by Year',
       caption = chart_cap,
       y = element_blank(),
       x = 'Point Spread')+
  theme_yaz()
ggsave('Point Spreads Ridgeline Plot.png', height = 7, width = 5)

results%>%
  group_by(year)%>%
  summarise(win_pct = mean(lower_seed_win)*100)%>%
  ggplot(aes(year, win_pct))+
  geom_line(color = yaz_cols[1])+
  stat_smooth(color = yaz_cols[3])+
  labs(title = 'Win Percentage of Lower-Seeded Team by Year',
       y = 'Lower Seed Win Percentage',
       x = 'Year',
       caption = chart_cap)+
  theme_yaz()+
  scale_x_continuous(breaks = seq(1986,2018,4))+
  ylim(0,80)
ggsave('Win Percentage of Lower-Seeded Team by Year.png', width = 6, height = 4)

results%>%
  count(winner_seed)%>%
  # group_by(winner_seed, round)%>%
  # mutate(n_games = n())%>%
  # ungroup()%>%
  # mutate(win_pct = round(n*100/n_games,2))%>%
  ggplot(aes(x = winner_seed, y = n))+
  geom_col(fill = yaz_cols[1])+
  scale_x_continuous(breaks = seq(1,16,1))+
  labs(title = 'Wins by Seed - 1985 to 2018',
       y = 'Wins Since 1985',
       x = 'Seed',
       caption = chart_cap)+
  theme_yaz()
ggsave('Wins by Seed Since 1985.png', width = 6, height = 4)
```

# How Well Does Seed Model Win Probability?
Build an overall logistic regression model of win probability by seed. Being one seed higher offers an 18
```{r}
alpha_results <- results%>%
  mutate(a_seed = ifelse(winner_name < not_winner_name, 
                         (winner_seed - not_winner_seed)*-1,
                         (not_winner_seed - winner_seed)*-1),
         a_winner = ifelse(winner_name < not_winner_name, 1, 0))

prob.fit <- glm(a_winner ~ a_seed, data = alpha_results, family = 'binomial')
prob.fit1 <- glm(a_winner ~ a_seed, data = alpha_results%>%filter(round_number == 0), family = 'binomial')
prob.fit2 <- glm(a_winner ~ a_seed, data = alpha_results%>%filter(round_number == 1), family = 'binomial')
prob.fit3 <- glm(a_winner ~ a_seed, data = alpha_results%>%filter(round_number == 2), family = 'binomial')
prob.fit4 <- glm(a_winner ~ a_seed, data = alpha_results%>%filter(round_number == 3), family = 'binomial')

seed_odds <- ((confint.default(prob.fit)%>%exp()-1)*100)[2,]
rnd1_odds <- ((confint.default(prob.fit1)%>%exp()-1)*100)[2,]
rnd2_odds <- ((confint.default(prob.fit2)%>%exp()-1)*100)[2,]
rnd3_odds <- ((confint.default(prob.fit3)%>%exp()-1)*100)[2,]
rnd4_odds <- ((confint.default(prob.fit4)%>%exp()-1)*100)[2,]

win_probs <- data.frame(round(rbind(seed_odds, rnd1_odds, rnd2_odds, rnd3_odds, rnd4_odds)),
                        round = c('Overall','First Round','Second Round','Sweet 16','Elite 8'),
                        order = seq(5,1))%>%
  select(round, order, lo = X2.5.., hi = X97.5..)

ggplot(win_probs, aes(x = reorder(round, order), y = lo))+
  geom_errorbar(aes(ymin = lo, ymax = hi),
                size = 1, width = 0.15,
                color = yaz_cols[1])+
  labs(title = 'Marginal Win Probability of a One Seed Advantage',
       y = 'Marginal Effect',
       x = element_blank(),
       caption = chart_cap)+
  theme_yaz()+
  coord_flip()
ggsave('Marginal Win Probability of a One Seed Advantage.png', height = 3, width = 6)
```

The number of games is probably too small to go much past the Sweet 16, but the overall model should be interesting to look at over time.
```{r}
year_lo <- c()
year_pe <- c()
year_hi <- c()
for(i in seq(1,length(unique(alpha_results$year)))){
  tourney_year <- alpha_results%>%filter(year == unique(alpha_results$year)[i])
  prob.fit.time <- glm(a_winner ~ a_seed, data = tourney_year, family = 'binomial')
  year_lo[i] <- ((confint.default(prob.fit.time)%>%exp()-1)*100)[2,1]
  year_pe[i] <- ((prob.fit.time$coefficients%>%exp()-1)*100)[2]
  year_hi[i] <- ((confint.default(prob.fit.time)%>%exp()-1)*100)[2,2]
}

win_probs_time <- data.frame(lo = year_lo,
                        pe = year_pe,
                        hi = year_hi,
                        year = unique(alpha_results$year))%>%
  select(year, lo, pe, hi)

ggplot(win_probs_time, aes(x = year, y = pe))+
  geom_ribbon(aes(ymin = lo, ymax = hi),
              alpha = .5,
              fill = yaz_cols[3])+
  geom_line(color = yaz_cols[4])+
  geom_hline(yintercept = ((prob.fit$coefficients%>%exp()-1)*100)[2],
             linetype = 'dashed')+
  annotate('text', x = 2019, y = 35, label = 'Dashed Line is Average', angle = 90, size = 2.5)+
  labs(title = 'Marginal Benefit of Better Seed by Year',
       y = 'Marginal Benefit', x = element_blank(),
       caption = chart_cap)+
  theme_yaz()+
  xlim(1985,2019)+
  scale_x_continuous(breaks = seq(1985,2019,5))
ggsave('Marginal Benefit of Better Seed by Year.png', height = 4, width = 6)
```

# How well does seed explain the number of games won
Simply using seed as a predictor in a negative binomial regression model produces remarkably good estimates of number of games won by team. 
```{r}
n_wins_df <- results%>%
  filter(round_number <= 3)%>%
  count(year, winner_name, winner_seed)

nb.fit <- glm.nb(n ~ winner_seed, data = n_wins_df)

win_n_time <- predict(nb.fit, n_wins_df, type = 'response')

wins_by_seed <- bind_cols(n_wins_df, data.frame(n_predicted = round(win_n_time)))

ggplot(wins_by_seed%>%
         group_by(winner_seed)%>%
         summarise(n_won = sum(n),
                   n_pred = sum(round(n_predicted)))%>%
         reshape2::melt(id.vars = 'winner_seed'), 
       aes(x = winner_seed, y = value, fill = variable))+
  geom_col(position = position_dodge())+
  scale_fill_manual(name = element_blank(),
                    values = yaz_cols[3:4],
                    labels = c('Actual','Predicted'))+
  theme_yaz()+
  labs(title = 'Predicted vs. Actual Wins by Seed: 1985-2018',
       x = 'Seed', y = 'Number of Wins')+
  scale_x_continuous(breaks = seq(1,16))
ggsave('Predicted vs Actual Wins by Seed.png', height = 4, width = 6)

difference_by_year <- wins_by_seed%>%
  group_by(year, winner_seed)%>%
  summarise(diff = sum(n_predicted)- sum(n))

add_rows <- list() 

for(i in seq(1985,2018)){
  df <- difference_by_year%>%filter(year == i)
  missing_seeds <- setdiff(seq(1,16), unique(df$winner_seed))
  extra_rows <- data.frame(year = rep(i,length(missing_seeds)),
                           winner_seed = missing_seeds)
  missing_difference <- round(predict(nb.fit, extra_rows, type = 'response'))
  
  add_rows[[i]] <- bind_cols(extra_rows, data.frame(diff = missing_difference))
}

ggplot(difference_by_year%>%bind_rows(add_rows), aes(x = year, y = -diff))+
  facet_wrap(~winner_seed)+
  geom_hline(yintercept = 0, color = yaz_cols[3], linetype = 'dashed')+
  geom_line(color = yaz_cols[1])+
  labs(title = 'Games Won Relative To Expectations by Year and Seed',
       y = 'Games Won Relative to Expectation',
       x = 'Year')+
  theme_yaz()+
  theme(axis.line = element_line())+
  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf)+
  scale_x_continuous(breaks = seq(1985,2018,5), 
                     labels = substring(seq(1985,2018,5),3,4))
ggsave('Games Won Relative To Expectations by Year and Seed.png')
```

